Vertical and oblique transmission with fluctuating transmission

### 2018-05-30 ms/ms_sunnyvale.tex
symmetric migartion

\documentclass[12pt]{extarticle}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
headheight=12pt
}

@@

\paragraph{Unconditional migration and symmetric selection.}

For the simple case of unconditional migration $m_1=m_2=m<1/2$ \citep{McPeek1992} after symmetric selection $w_1=1/w_2=w>1$, the recursions~\eqref{eq:migration_model} become
\begin{equation}\begin{aligned} \label{eq:migration_model_unconditional_symmetric}
x_1'' &= (1-m)x_1\Big(\rho_1 \frac{w}{\overline w_1} x_1 + 1-\rho_1 \Big) + m x_2\Big(\rho_2 \frac{1/w}{\overline w_w} x_2 + 1-\rho_2 \Big), \\
x_2'' &= m x_1\Big(\rho_1 \frac{w}{\overline w_1} x_1 + 1-\rho_1 \Big) + (1-m) x_2\Big(\rho_2 \frac{1/w}{\overline w_w} x_2 + 1-\rho_2 \Big).
\end{aligned}
\end{equation}

>>>>

\documentclass[14pt]{extarticle}
\usepackage{geometry}
\geometry{
a4paper,
total={170mm,257mm},
left=20mm,
top=20mm,
headheight=12pt
}

@@

\paragraph{Symmetric migration and selection.}

For the simple case of symmetric migration $m_1=m_2=m<1/2$ after symmetric selection $w_1=1/w_2=w>1$, the recursions~\eqref{eq:migration_model} become
\begin{equation}\begin{aligned} \label{eq:migration_model_unconditional_symmetric}
x_1'' &= (1-m)x_1\Big(\rho_1 \frac{w}{\overline w_1} x_1 + 1-\rho_1 \Big) + m x_2\Big(\rho_2 \frac{1/w}{\overline w_w} x_2 + 1-\rho_2 \Big), \\
x_2'' &= m x_1\Big(\rho_1 \frac{w}{\overline w_1} x_1 + 1-\rho_1 \Big) + (1-m) x_2\Big(\rho_2 \frac{1/w}{\overline w_w} x_2 + 1-\rho_2 \Big).
\end{aligned}
\end{equation}
